Checklist

### 2019-04-26 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] equipment ids

\parindent=0pt
\title{Checklist}
\date{August 2nd, 2017}
\begin{document}

\Person{Yichao}{
  Equipments and power supplies are mostly located around the laser table on the library side.\\
  Check Lee's part after everything are off.
}
\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{UPS}{
  \textbf{2nd level above laser table}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}
\Person{Jon}{
  Equipments and power supplies are mostly located around the machine table facing the laser table
  or the computer area.\\
  Check Jessie's part after everything are off.
}
\subsection{Equipments}
\DevDef{Agilent function generator for Na 1.0 switching}{
  \textbf{1st level above TiSapph facing computers}\\
  Record parameters:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 2 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
}
\DevDef{Tweezer 3 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
}
\Person{Lee}{
  Equipments and power supplies are mostly located around the laser table
  on the computer area side.\\
  Check Yichao's part after everything are off.
}
\subsection{Equipments}
\DevDef{PLL for 1.0 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{PLL for 1.0 Cs Raman}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Switch off/on the front switch
}
\DevDef{1st version Till's current controller for Cs MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Cs 1.0 MOT lock box}{
  \textbf{1st level above Cs MOT lasers}
  \begin{itemize}
  \item\OffBox Make sure the laser is unlocked.
  \end{itemize}
}
\DevDef{Novatech function generator}{
  \textbf{1st level above Cs MOT lasers}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Save settings
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Restore settings
  \end{itemize}
}
\DevDef{New Focus Cs Raman lasers drivers (2x)}{
  \textbf{1st level above Cs Raman lasers}\\
  Record Temperature, Current, Piezo voltage\\
  Temperature is accessible in the menu under system status\\

  \begin{tabular}{|c|c|}
    \hline
    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
    F3 Piezo Voltage&\\\hline
    F3 Temperature&\\\hline
    F4 Current&\\\hline
    F4 Piezo Voltage&\\\hline
    F4 Temperature&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox (Turn on)
  \end{itemize}
}
\DevDef{SRS shutter driver for Cs}{
  \textbf{1st level above Cs Raman lasers}\\
  Switch off/on with the switch on the back.
}
\DevDef{New Focus lock box for Cs Raman}{
  \textbf{1st level above Cs Raman lasers}\\
  Unplug power.
}
\DevDef{Homebuilt temperature servo for Cs tweezer}{
  \textbf{1st level above Cs tweezer}\\
  Switch off/on the front switch
}
\DevDef{2nd version Till's current controller for Cs Tweezer}{
  \textbf{1st level above Cs tweezer}\\
  Record current value:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Thorlabs current controller}{
  \textbf{1st level below Cs tweezer driver}\\
  Unused\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
}
\DevDef{Thorlabs temperature controller for Cs tweezer}{
  \textbf{1st level above Cs tweezer}\\
  Record temperature settings\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Intensity servo for Cs}{
  \textbf{1st level above Cs tweezer}\\
  Unplug power
}
\subsection{Power supplies}
\DevDef{Benchtop power supply}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above Cs tweezer/MOT lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply}{
  \textbf{1st level next to Cs Raman driver}\\
  Record voltage/current values:\\

>>>>

\parindent=0pt
\title{Checklist}
\date{April 27th, 2019}
\begin{document}

\onecolumn
\Person{Yichao}{
  Equipments and power supplies are mostly located around the laser table facing the wall.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Laser table facing computer or the wall} west $\rightarrow$ south}\\\hline
  1&Benchtop power for Cs MOT beat lock&Lv1 above 1.0 Cs MOT\\\hline
  2&PLL for Cs MOT&Below Cs MOT\\\hline
  3&Home power (+-15,5)&Lv2 above Cs MOT\\\hline
  4&Valan&1.5 amplifier stack Lv1 above 1.0 Cs MOT\\\hline
  5&Till driver v2 for 1.5 Na Raman&Lv1 above 1.5 Na Raman\\\hline
  6&Temp servo for 1.5 Na Raman seed&Lv1 above 1.5 Na Raman\\\hline
  7&Temp servo for 1.5 Na Raman doubler&Lv1 above 1.5 Na Raman\\\hline
  8&PLL for Cs Raman&Next to 1.0 Cs Raman\\\hline
  9&New Focus driver for Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
  10&Benchtop power (x3)&Lv2 above 1.0 Cs MOT\\\hline
  11&Home power (24V) x2&Lv2 above 1.0 Cs Raman\\\hline
  12&Benchtop power&Lv1 next to New Focus driver\\\hline
  13&Shutter driver&Lv1 above 1.0 Cs Raman\\\hline
  14&New Focus lock box for 1.0 Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
  15&Thorlabs temp servo for 1.0 Na Raman doubler&Lv1 above 1.0 Na seed\\\hline
  16&Timebase drivers for 1.0 Na Raman and Na D2&Lv1 above Thorlabs temp servo\\\hline
  17&Benchtop power for 1.0 Cs Raman&Lv2 above New Focus lock box\\\hline
  18&High voltage power&Lv2 above timebase drivers\\\hline
  19&Home lock box for Na D2&Lv1 above 1.0 Na seed\\\hline
  20&MPB Raman laser&Lv1 above 1.0 Na MOT\\\hline
  21&Oscilloscope for Na D2 lock&Lv1 above MPB Raman laser\\\hline
  22&Benchtop power for 1.0 Na Raman seed&Lv2 above oscilloscope\\\hline
\end{longtable}
\twocolumn

\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{UPS}{
  \textbf{2nd level above laser table}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}

\onecolumn
\Person{Kenneth}{
  Equipments and power supplies are mostly located between the machine table and the laser table.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Laser table side facing machine table} north $\rightarrow$ east}\\\hline
  1&671 EOM stack&Floor\\\hline
  2&1550 Amp&Floor\\\hline
  3&Radio computer&Lv2\\\hline
  4&Benchtop power&Lv2 next to radio computer\\\hline
  5&High voltage power&Lv2 next to benchtop power\\\hline
  6&Variac for Na cell&Lv1 above 1.0 Na MOT\\\hline
  7&Shutter driver&Lv1 next to variac\\\hline
  8&Home lock box for 1.0 Na D1&Lv1 next to shutter driver\\\hline
  9&1038 Amp&Floor\\\hline
  10&1038 Timebase laser&Table\\\hline
  11&FPGA box for 1.0&Lv2\\\hline
  12&Thorlabs temp servo for Na D1 doubler&Lv1 above Na D1\\\hline
  13&Thorlabs temp servo for Na D1 seed&Lv1 above Na D1\\\hline
  14&Thorlabs current for Na D1 seed&Lv1 above Na D1\\\hline
  15&Benchtop power&Lv2 above Thorlabs controllers for Na D1 seed\\\hline
  16&Home power (24)&Lv2 next to benchtop power\\\hline
  17&Benchtop power x2&Lv2 next to Home power (24)\\\hline
  18&Till driver v2 for 976&Lv1 above Na D1 doubler\\\hline
  19&Thorlabs temp servo for Cs tweezer&Lv1 above Timebase 1038 beam\\\hline
  20&Thorlabs current (2A) (off)&Lv1 above Thorlabs temp servo\\\hline
  21&Till driver v2 for 671&Lv1 above Thorlabs current\\\hline
  22&Home temp servo x2&Lv1 above Timebase 1038 control box\\\hline
  23&Oscilloscope&Lv1\\\hline
  \multicolumn{3}{|c|}{\textbf{Machine table side facing laser table} south}\\\hline
  24&Thorlabs current for 1.5 Cs MOT&Lv1 above 1.5 Cs\\\hline
  25&Till driver v2 for 1.5 Cs RP&Lv1 above 1.5 Cs\\\hline
  26&Home temp servo (x2) for 1.5 Cs MOT/RP&Lv1 above 1.5 Cs\\\hline
  27&Oscilloscope for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
  28&Home lock box for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
  29&Novatec for 1.5 Cs lock&Lv1 above 1.5 Cs\\\hline
  30&Benchtop power&Lv2 1.5 Cs MOT/RP current\\\hline
  31&Home power (24) x2&Lv2 next to benchtop power\\\hline
  32&Benchtop power&Lv2 on two home power (24)\\\hline
  33&Home power (+-15,5)&Lv2 middle\\\hline
  34&Benchtop power (x2) for uWave Amp&Lv2 next to home power (+-15,5)\\\hline
  35&Benchtop power (x2)&Lv1 above 1.5 Na\\\hline
  36&High voltage power&Lv1 next to 2 benchtop power\\\hline
  37&Function generator for 1.0 MOT piezo&Lv1\\\hline
  38&Temperature and pump controllers for cavity&Lv1 next to function generator\\\hline
  39&Water chiller for uWave breadboard&Floor\\\hline
  40&SAES pump&Lv1 above 1.0 chamber\\\hline
  41&Benchtop power x2&Lv2 next to coil servo\\\hline
\end{longtable}
\twocolumn
\subsection{Equipments}
\DevDef{Agilent function generator for Na 1.0 switching}{
  \textbf{1st level above TiSapph facing computers}\\
  Record parameters:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 2 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
}
\DevDef{Tweezer 3 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
}

\onecolumn
\Person{Jessie}{
  Equipments and power supplies are mostly located between the machine table and the 1.5 table.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Machine table Facing the wall} north}\\\hline
  1&Benchtop power&Lv2\\\hline
  2&Home power (24)&Lv2 above 1.0 tweezer breadboard\\\hline
  3&Home power (+-15,5)&Lv2 above home power (24)\\\hline
  4&Benchtop power x9&Lv2 next to home power (24) and (+-15,5)\\\hline
  5&Current servo for compensation coil&Lv1 below home power (24)\\\hline
  6&Kenneth servo for 1.0 Cs tweezer&Lv1\\\hline
  7&High voltage Amp for 630 lock&Lv1\\\hline
  8&Vincent servo x2 for STIRAP lasers&Lv1\\\hline
  9&Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos\\\hline
  10&Rack for STRAP&Lv1 next to Vincent servos\\\hline
  11&Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5\\\hline
  12&Home temp servo x3 for STIRAP&Lv2 next to 9x benchtop power\\\hline
  13&FPGA box for 1.5&Lv2\\\hline
  14&Home power (+-15,5)&Lv2 next to FPGA box\\\hline
  15&Benchtop power x2&Lv2 on home power (+-15,5)\\\hline
  16&Benchtop power&Lv2 next to home power (+-15,5)\\\hline
  17&Benchtop power&Floor rack Lv1\\\hline
  18&Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  19&Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers\\\hline
  20&Benchtop power&Floor rack Lv2 next to Till drivers\\\hline
  21&Home temp servo x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
  22&Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos\\\hline
  23&Delay generator for 1.5 Na&Lv1 below 1.5 output panel\\\hline
  24&Till driver v2 for 1.0 Innolume&Lv1 next to delay generator\\\hline
  25&Kenneth servo for 1.5 tweezers&Lv1\\\hline
  26&Home temp servo for 1.0 Innolume&Lv1\\\hline
  27&Shutter driver&Lv1 on M2 controller\\\hline
  28&TiSapph&Floor\\\hline
  29&Function generator for 1.0 Na switching&Lv1 above TiSapph\\\hline
  30&Keithley power for 1.0 Innolume&Lv2 above TiSapph\\\hline
  31&Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT\\\hline
  32&Home temp servo for 1.0 Cs MOT&Lv2 on Till driver v2\\\hline
  33&Benchtop power&Lv2 facing computer\\\hline
  34&High voltage power&Above Lv2 on power outlet\\\hline
  \multicolumn{3}{|c|}{1.5 Rack}\\\hline
  35&Home power (24)&Bottom level\\\hline
  36&SEAS pump controller&Middle left\\\hline
  37&Benchtop power&Middle next to pump controller\\\hline
  38&Oscilloscope for 1.5 monitor&Above pump controller\\\hline
  39&Benchtop power for 1.5 coil&Above oscilloscope\\\hline
  40&High voltage Amp for 1.5 MOT piezo&Top level\\\hline
  41&Function generator for 1.5 MOT piezo&Top level on high voltage Amp\\\hline
  \multicolumn{3}{|c|}{Below 1.5 table}\\\hline
  42&Benchtop power x3&Near outer edge\\\hline
  43&IGBT stack&Floor\\\hline
  44&LED driver&Near inner edge\\\hline
  45&AWG computer&Floor\\\hline
  \multicolumn{3}{|c|}{Above 1.5 table}\\\hline
  46&Benchtop power&Lv1\\\hline
  47&Benchtop power&Lv2\\\hline
  48&Radio computer&Lv2\\\hline
\end{longtable}
\twocolumn

\subsection{Equipments}
\DevDef{TiSapph}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off pump, unplug from wall
  \item\OffBox Turn off controller, unplug from wall
  \item\OffBox Turn off chiller, unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall, turn on chiller
  \item\OnBox Plug into wall, turn on controller
  \item\OnBox Plug into wall, turn on pump
  \end{itemize}
}
\DevDef{Quantel Laser}{
  \textbf{1st level in the middle, facing 1.5 table}\\
  Ask Frederic.
  \vspace{1cm}
}
\DevDef{Intensity servo for Na}{
  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
  Unplug power
}
\DevDef{1st version Till's current controller for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  Switch off/on the front switch
}
\DevDef{PLL for 1.5 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings ???
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for dispensers}{
  \textbf{1st level above NaCs 1.0 chamber}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for 1.5 computer control clock}{
  \textbf{2nd level next to 1.5 computer control box}\\
  Record voltage/current values:\\
